# Homework 6 - Savannah Harrison

# Task 1: Conceptual Questions

1.  What is the purpose of the lapply() function? What is the equivalent purrr function?

    **The lapply() function is used to apply a function to all elements of a list and it returns a list object of the same length. The equivalent purrr function is purrr::map().**

2.  Suppose we have a list called my_list. Each element of the list is a numeric data frame (all columns are numeric). We want use lapply() to run the code cor(numeric_matrix, method = "kendall") on each element of the list. Write code to do this below! (I’m really trying to ask you how you specify method = "kendall" when calling lapply())

**lapply(my_list, function(df) cor(df, method = "kendall"))**

3.  What are two advantages of using purrr functions instead of the BaseR apply family?
**Using the purrr functions allows for greater consistency between functions and they have lots of helper functions that are useful.**

4.  What is a side-effect function?
**A side-effect function (ex: print(), write_csv()) doesn't change the data, it just tries to produce something.**

5.  Why can you name a variable sd in a function and not cause any issues with the sd function?
**When a function is called, there is a temperary function environment. Variables inside of functions do not exist outside of the function, which is why if you name a variable sd it will not translate outside of the function. It will go back to its built-in meaning.**

# Task 2: Writing R Functions
Writing RMSE function.
```{r}
getRMSE <- function(responses, predictions, ...) {
  if (length(responses) != length(predictions)) {
    stop("Responses and predictions must have same length.")
  }
  squared_diffs <- (responses-predictions)^2
  
  mean_squared_error <- mean(squared_diffs, ...)
  
  RMSE <- sqrt(mean_squared_error)
  
  return(RMSE)
  }
```
Creating response values and predictions to test.
```{r}
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10 * x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))
```
Testing RMSE function with created data.
```{r}
RMSE1 <- getRMSE(resp, pred)
print(RMSE1)
```
Replacing two response values with NA.
```{r}
resp_with_na <- resp
resp_with_na[1] <- NA_real_
resp_with_na[2] <- NA_real_
```
Testing without specifting behavior for NA.
```{r}
RSME2 <- getRMSE(resp_with_na, pred)
print(RSME2)
```
Testing with specifting behavior for NA.
```{r}
RSME3 <- getRMSE(resp_with_na, pred, na.rm = TRUE)
print(RSME3)
```
Creating MAE function.
```{r}
getMAE <- function(responses, predictions, ...) {
   if (length(responses) != length(predictions)) {
    stop("Responses and predictions must have same length.")
  }
  diffs <- abs(responses-predictions)
  
  MAE <- mean(diffs,...)
  
  return(MAE)
}
```
Creating response values and predictions to test MAE function.
```{r}
set.seed(10)
n <- 100
x <- runif(n)
resp2 <- 3 + 10 * x + rnorm(n)
pred2 <- predict(lm(resp ~ x), data.frame(x))
```
Testing MAE function using the data.
```{r}
MAE1 <- getMAE(resp2, pred2)
print(MAE1)
```
Replacing two response values with missing values.
```{r}
resp_with_na2 <- resp2
resp_with_na2[1] <- NA_real_
resp_with_na2[2] <- NA_real_
```
Testing without specifting behavior for NA.
```{r}
MAE2 <- getMAE(resp_with_na2, pred2)
print(MAE2)
```
Testing with specifting behavior for NA.
```{r}
MAE3 <- getMAE(resp_with_na2, pred2, na.rm = TRUE)
print(MAE3)
```
Creating metrics wrapper function to get either or both metrics.
```{r}
getMetrics <- function(responses, predictions, metrics = c("RMSE", "MAE"),...) {
  if(!is.vector(responses) || !is.vector(predictions) ||
     !is.atomic(responses) || !is.atomic(predictions) ||
     !is.numeric(responses) || !is.numeric(predictions)) {
       stop("Responses and predictions must be numeric atomic vectors.")
     }
     
results <- list()
     
  if("RMSE" %in% metrics) {
    results$RMSE <- getRMSE(responses, predictions, ...)
  }
  if("MAE" %in% metrics) {
    results$MAE <- getMAE(responses, predictions, ...)
  }

return(results)
}
```
Creating response values and predictions to test.
```{r}
set.seed(10)
n <- 100
x <- runif(n)
resp3 <- 3 + 10 * x + rnorm(n)
pred3 <- predict(lm(resp ~ x), data.frame(x))
```
Testing the function with "RMSE".
```{r}
Metrics1 <- getMetrics(resp3, pred3, "RMSE")
print(Metrics1)
```
Testing the function with "MAE".
```{r}
Metrics2 <- getMetrics(resp3, pred3, "MAE")
print(Metrics2)
```
Specifying both metrics.
```{r}
Metrics3 <- getMetrics(resp3, pred3, )
print(Metrics3)
```
Replacing two repsonse values with missing values.
```{r}
resp_with_na3 <- resp3
resp_with_na3[1] <- NA_real_
resp_with_na3[2] <- NA_real_
```
Testing the function with the missing values.
```{r}
Metrics4 <- getMetrics(resp_with_na3, pred3, "RMSE")
print(Metrics4)
```
```{r}
Metrics5 <- getMetrics(resp_with_na3, pred3, "RMSE", na.rm = TRUE)
print(Metrics5)
```

```{r}
Metrics6 <- getMetrics(resp_with_na3, pred3, "MAE")
print(Metrics6)
```

```{r}
Metrics7 <- getMetrics(resp_with_na3, pred3, "MAE", na.rm = TRUE)
print(Metrics7)
```

```{r}
Metrics8 <- getMetrics(resp_with_na3, pred3,)
print(Metrics8)
```

```{r}
Metrics9 <- getMetrics(resp_with_na3, pred3, na.rm = TRUE)
print(Metrics9)
```
Testing the function by passing in incorrect data.
```{r}
Metrics5 <- getMetrics(iris)
```
# Task 3: Querying an API and a Tidy-Style Function

```{r}
install.packages("jsonlite")
```

```{r}
library(httr)
library(dplyr)
library(purrr)
library(jsonlite)
```


```{r}
teslaurl <- "https://newsapi.org/v2/everything?q=tesla&from=2024-09-15&sortBy=publishedAt&apiKey=c36df82613354f00b6331308d41865d6"
teslareturn <- httr::GET(teslaurl)
parsedtesla <- fromJSON(rawToChar(teslareturn$content))
teslastats <- as_tibble(parsedtesla)
articles <- pluck(parsedtesla$articles$content)
```


```{r}
articles
```

```{r}
getNews <- function(subject, time_period, API_key) {
  url <- "https://newsapi.org/v2/everything"
  response <- httr::GET(url, query = list( 
    q = subject,
    from = time_period,
    apiKey = API_key))
  
   if (status_code(response) == 200) {
     news_data <- content(response, as = "parsed", type = "application/json")
     
    articles <- news_data$articles
    articles_df <- as.data.frame(articles)
     return(articles_df)
  } else {
    return(paste("Error:", status_code(response)))
  }
}
```

```{r}
API_key <- "c36df82613354f00b6331308d41865d"
```

```{r}
result <- getNews("Tesla", "2024-09-15", API_key)
```

